Supplementary Information

### 2021-06-03 doc/manuscript/ForestGEO_treerings_SI.Rmd
fix page breaks
#130

![ `r `](tables_figures/SI_figures/GLS_pre1970_ScottyCreek.png){ width=57% }

@@

![`r SC_1970break_legend` *Climwin*-selected climate drivers are coded on the x-axes as the climate variable name followed by the range of months (p=previous year, c=current year) over which it is most influential. For each relationship shown, other terms in the model are held constant at their median. Best-fit polynomials are plotted with solid lines when both first- and second-order terms are significant (t-test’s p-value <0.05), dashed lines when only one term is significant, and dotted lines when neither is significant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate driver, shading indicates 1 SD.](tables_figures/SI_figures/GLS_post1970_ScottyCreek.png){ width=57% }

## `r RW_interactions_all_legend`

>>>>

![ `r `](tables_figures/SI_figures/GLS_pre1970_ScottyCreek.png){ width=50% }

@@

![`r SC_1970break_legend` *Climwin*-selected climate drivers are coded on the x-axes as the climate variable name followed by the range of months (p=previous year, c=current year) over which it is most influential. For each relationship shown, other terms in the model are held constant at their median. Best-fit polynomials are plotted with solid lines when both first- and second-order terms are significant (t-test’s p-value <0.05), dashed lines when only one term is significant, and dotted lines when neither is significant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate driver, shading indicates 1 SD.](tables_figures/SI_figures/GLS_post1970_ScottyCreek.png){ width=50% }

\newpage
## `r RW_interactions_all_legend`
